Report on Late Winter2013 Production: Image Differencing

### 2013-03-28 W13report.tex
Added discussion of edge detections.

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
difference images to associate the DiaSources with Sources in the
images, and also use a 3'' association with the input source catalog
to define matches and orphans.  Associations are listed in the
N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched
false positives in the N$_{Orphan}$ column.  The former are likely to
come from systematics in the subtractions of stars, while the latter
would be due to fluctuations in the background.  We note 2 effects
that will impact N$_{Match}$.  The first is that, with a 3'' matching
radius, 4\% of random fluctuations will by--chance associate with a
Source.  Assuming that N$_{Orphan}$ represents 96\% of the background
fluctuation population, we estimate the number of fluctuations from
that same population that would have associated with Sources as
N$_{Random}$.  Finally, we count all matches that occur within 100
pixels of the image boundary, where we might expect the spatial
extrapolation to yield systematic residuals, as N$_{D<100}$.  To the
extent that (N$_{Random}$ + N$_{D<100}$) $<$ N$_{Match}$, we have a
small residual set of systematic false detections in our imaging
ensemble.  Aside from the deconvolution run, this is at the level of
10 total false detections over 9 sensors in 5 production runs, or 1
every 4--5 images.

@@

We have examined the distribution of these false detections across the
image, and find no significant overdensities near the borders of the
images, which would be expected in cases of under or over--fitting of
the various spatial models (astrometry, backgrounds, PSF--matching
kernels).  Figure~\ref{edgedist} provides the distribution of
distances from the edge of the sensor for all false detections in {\it
  blue}, with a random sample of points in the image given in {\it
  green}.  Uncertainties are plotted using the square root of the
number of points in each bin, and the histograms are normalized to
provide a probability density.  The takeaway is that we find no
significant correlation of false detections with the boundaries of the
fitting functions.

@@

We intend to research additional aspects of the problem going forward,
including:
\begin{itemize}
\item How the false detection rate varies with more realistic SEDs;
\item How the false detection rate varies with airmass;
\item How the system behaves with a realistic mix of stars and galaxies;
\item How the false detection rate looks in crowded fields;
\item How to perform measurement on pre--filtered difference images;
\end{itemize}

Gaussian processes.
Measuremnt positive and negative asymmetry.
Measurement on prefiltered data.
Configure on the fly based on conditoins.

@@

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from
  detection and measurement, for the {\bf prefiltering} pipeline.
  Results for visit v6866601 are shown as {\it red squares}, for
  v6866602 as {\it green circles}, and for v6866603 {\it blue
    triangles}.  Three of the statistics, descibed in
  Section~\ref{sec-stats}, are presented.  They clearly correlate with
  each other (leftmost panels), and also tend to correlate with the
  number of false detections (rightmost column).}
\label{corrpre}
\end{figure}

>>>>

The numbers of false detections in each best case are given in
Table~\ref{tab-bestfp10}.  We undertook a manual inspection of all
difference images to associate the DiaSources with Sources in the
images, and also use a 3'' association with the input source catalog
to define matches and orphans.  Associations are listed in the
N$_{Match}$ column of Table~\ref{tab-bestfp10}, with the unmatched
false positives in the N$_{Orphan}$ column.  The former are likely to
come from systematics in the subtractions of stars, while the latter
would be due to fluctuations in the background.  We note 2 effects
that will impact N$_{Match}$.  The first is that, with a 3'' matching
radius, 4\% of random fluctuations will by--chance associate with a
Source.  Assuming that N$_{Orphan}$ represents 96\% of the background
fluctuation population, we estimate the number of fluctuations from
that same population that would have associated with Sources as
N$_{Random}$.  Finally, we count all matches that occur within 100
pixels of the image boundary, where we might expect deficiencies in
the various spatial extrapolations (astrometry, backgrounds,
PSF--matching kernels) to yield systematic residuals, as N$_{D<100}$.
Figure~\ref{edgedist} provides the distribution of distances from the
edge of the sensor for all false detections in {\it blue}, with a
random sample of points in the image given in {\it green}.
Uncertainties are plotted using the square root of the number of
points in each bin, and the histograms are normalized to provide a
probability density.  Aside from the deconvolution reduction, we find
no significant correlation of false detections with the boundaries of
the fitting functions.  To the extent that N$_{Random}$ $<$
N$_{Match}$, we have a small residual set of systematic false
detections in our imaging ensemble.  Aside from the deconvolution run,
this is at the level of 10 total false detections over 9 sensors in 5
production runs, or 1 every 4--5 images.

@@

@@

We intend to research additional aspects of the problem going forward,
including:
\begin{itemize}
\item How the false detection rate varies with more realistic SEDs;
\item How the false detection rate varies with airmass;
\item How the system behaves with a realistic mix of stars and galaxies;
\item How the false detection rate looks in crowded fields;
\item How to perform measurement on pre--filtered difference images;
\item Adoption of Gaussian processes for spatial modeling of the kernel;
\item Investigating the differences in measurement on positive/negative sources;
\item Developing a measurement suite for sources in prefiltered data;
\item Determing how much ``on the fly'' configuration we may do to optimize PSF--matching.
\end{itemize}

@@

\begin{figure}
\centering{\includegraphics[width=0.9\textwidth]{figures/corrB.eps}} \\
\caption{Correlation of the statistics calculated on the control
  sample {\tt KernelCandidates} during the model fitting with the
  number of false positives per sensor coming from detection and
  measurement, for the {\bf prefiltering} pipeline.  Results for visit
  v6866601 are shown as {\it red squares}, for v6866602 as {\it green
    circles}, and for v6866603 {\it blue triangles}.  Three of the
  statistics, descibed in Section~\ref{sec-stats}, are presented.
  They clearly correlate with each other, and also tend to correlate
  with the number of false detections (bottom row).}
\label{corrpre}
\end{figure}
